Reproducible Research in R: A tutorial on how to do the same thing more than once

### 2021-10-05 manuscript.Rmd
add section when pac is applicable

>>>>

#### When is PAC applicable

Every study that can be preregistered, can be preregistered with PAC.
One significant difference is that PAC demands a comprehensive analysis plan.
With traditional preregistration, however, the researcher gets away with deciding details later.
Some researchers may not feel ready to decide every detail.
In such case, we recommend to decide based on the best available knowledge and if these decisions prove infeasible, revise and explain them later as described in the section [Deviating from the preregistration and exploration].

Two applications, however, lend themselves to PAC.
First, registrations of clinical trials typically describe analyses in excruciating detail.
Those registrations typically contain a detailed description of how results will be presented, including example tables and graphics.
PAC may significantly reduce the required workload while maintaining (and exceeding) the required standards for registering a clinical trial.

Second, preregistering explorative statistical models (i.e. machine learning) is hardly feasible with standard preregistrations since they are too complex to describe and depend strongly on their software implementation verbally.
PAC, however, captures the precise algorithmic model, including its software implementation and is ideal for preregistering these models.
